Title Goes Here

### 2023-10-30 paper/main.tex
comments and sketching of evaluation

@@

@@

@@

@@

Our empirical evaluation demonstrates \system's ability to detect bugs in secure protocols. Our experiments are designed to answer two research questions:
%
\begin{itemize}
\item \textbf{RQ1:} Is \system capable of detecting insecurity in complex, multi-round protocols?
\item \textbf{RQ2:} Is \system capable of detecting insecurity in real-world protocols?
\end{itemize}
%
To answer RQ1, we generate \emph{random protocols} of varying sizes, and evaluate \system's ability to show they are insecure. The details appear in Section~\ref{sec:experiment-1:-random}. To answer RQ2, we evaluate \system on the case study protocols described in Section~\ref{sec:case-study-protocols}. The details appear in Section~\ref{sec:experiment-2:-real}. In both cases, \system is able to detect insecurity in the target protocols in under a minute.

@@

\paragraph{Experiment setup.}

\paragraph{Results.}

@@

\paragraph{Experiment setup.}

\paragraph{Results.}

>>>>

TODO: maybe say we invented these; give examples. Readers will assume these are existing terms if we don't say otherwise.

@@

TODO: maybe state it explicitly with the conditioning? Then we can say that no system can capture that property.

@@

TODO: Is efficient inference really necessary? The conditional independence test might be sufficient? I think we don't want to imply that inference is sufficient, because lots of work has done that

@@

TODO: maybe cite the Kifer work on property-based testing for DP (also a hyperproperty) and call out that our setting is (maybe) fundamentally high-dimensional so it's super tricky.

@@

Our empirical evaluation demonstrates \system's ability to detect bugs in secure protocols. Our experiments are designed to answer two research questions:
%
\begin{itemize}
\item \textbf{RQ1:} Is \system capable of detecting insecurity in complex, multi-round protocols?
\item \textbf{RQ2:} Is \system capable of detecting insecurity in real-world protocols?
\item \textbf{RQ3:} Is \system scalable to realistic protocols in reasonable time?
\end{itemize}
%
To answer RQ1, we generate \emph{random protocols} of varying sizes, and evaluate \system's ability to show they are insecure. The details appear in Section~\ref{sec:experiment-1:-random}. To answer RQ2, we evaluate \system on the case study protocols described in Section~\ref{sec:case-study-protocols}. The details appear in Section~\ref{sec:experiment-2:-real}. In both cases, \system is able to detect insecurity in the target protocols in under a minute.

@@

\paragraph{Experiment setup.}
In our first experiment, we generate random protocols and evaluate \system's ability to detect insecurity in these protocols. We randomly generate protocols according to the grammar of XXX. We bias the generated protocols in favor of generating and using randomness in each round of the protocol, in addition to the secret inputs. Random protocols of non-trivial length are extremely likely to be insecure.
%
We generate XXXX programs of size XXXX and evaluate \system's ability to detect insecurity.

\paragraph{Results.}
\emph{results description goes here}

@@

\paragraph{Experiment setup.}
In our second experiment, we evaluate \system's ability to detect insecurity in the real-world protocols described in Section~\ref{sec:case-study-protocols}. We run \system on the unmodified protocol in order to establish that the protocol is secure. Then, we mutate the protocol in several ways to introduce insecurity, and test \system's ability to detect it. Specifically, our mutations are:
%
\begin{itemize}
\item \textbf{Accidental secret}: accidentally sends a secret held by the honest party  to the corrupt party.
\item \textbf{Accidental gate}: accidentally sends an honest party's result from the evaluation of a multiplication gate to the corrupt party.
\item \textbf{Biased sharing}: uses biased randomness to construct secret shares of honest party inputs.
\item \textbf{Biased AND}: uses biased randomness as part of the evaluation of multiplication gates.
\end{itemize}
%
The severity of each mutation can be tuned by adjusting the bias in the related randomness. In the case of ``accidental secret'' and ``accidental gate,'' this affects the probability of accidentally revealing a value; in the others, it directly adjust the bias in the randomness.

\paragraph{Results.} \emph{results description goes here}

\subsection{Discussion}
